Hierarchical Dispatching and Overriding

### 2017-10-09 NewVersion/sections/Introduction.tex
Revised Intro

Closest to our work are mechanisms available in C++ and C\# that allow for two
unintentionally conflicting methods to coexist in a class. Among them, 
C++ is a representative that accepts the triangle inheritance and
resolves the ambiguity by \emph{static dispatching} or cast. But the drawback is that these conflicting methods cannot be further updated. 
% However, C++ has
% limited support for virtual methods with unintentional conflicts, and
% it will often throw errors when composing them. This is again
% unsatisfactory because virtual methods are pervasive in OOP and used 
% for code reuse and extensibility. A problem with the C++ approach is
% that programmers can only use either static or dynamic dispatching separately, but dealing
% with unintentional method conflicts seems to require a combination of
% both. 
Some other workarounds or approaches include delegation and
renaming/exclusion in the trait model. However renaming/exclusion 
can break the subtyping relation between a subclass and its parent.
This is not adequate for the class model commonly used in mainstream 
OOP languages, where the subclass is always expected to be a subtype 
of the parent class.

@@

This paper proposes \textit{hierarchical dispatching}: a novel approach
to method dispatching, which combines static and dynamic
information. Using hierarchical dispatching, the method binder will look
at both the \emph{static type} and the \emph{dynamic type} of the
receiver during runtime. When there are multiple branches that cause
unintentional conflicts, the static type can specify one branch among
them for unambiguity, and the dynamic type helps to find the most
specific implementation. In that case, both unambiguity and
extensibility are preserved. To present this idea, we introduce a
formalized model \MIM{} in Section~\ref{sec:formalization} based on
Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
proofs for type soundness. In the model we also propose
\textit{hierarchical overriding}, where method overriding can be applied
only to one branch of the class hierarchy. 
\name{} is partly inspired by the method resolution semantics
of C++, but it also incoorporates ideas from the trait model and Java
8's default methods.

>>>>

C++ and C\# do allow for two
unintentionally conflicting methods to coexist in a class. 
C++ accepts the triangle inheritance and
resolves the ambiguity by \emph{static dispatching} or casts. But the
drawback is that these conflicting methods cannot be further overriden. 
\bruno{how about C\#?}
% However, C++ has
% limited support for virtual methods with unintentional conflicts, and
% it will often throw errors when composing them. This is again
% unsatisfactory because virtual methods are pervasive in OOP and used 
% for code reuse and extensibility. A problem with the C++ approach is
% that programmers can only use either static or dynamic dispatching separately, but dealing
% with unintentional method conflicts seems to require a combination of
% both. 
Some other workarounds or approaches include delegation and
renaming/exclusion in the trait model. However renaming/exclusion 
can break the subtyping relation between a subclass and its parent.
This is not adequate for the class model commonly used in mainstream 
OOP languages, where the subclass is always expected to be a subtype 
of the parent class.

@@

This paper proposes two mechanisms to deal with unintentional method
conflicts: \textit{hierarchical dispatching} and \emph{hierarchical
  overriding}. Hierarchical dispatching is inspired by the mechanisms in C++ and
provides an approach
to method dispatching, which combines static and dynamic
information. Using hierarchical dispatching, the method binder will look
at both the \emph{static type} and the \emph{dynamic type} of the
receiver during runtime. When there are multiple branches that cause
unintentional conflicts, the static type can specify one branch among
them for unambiguity, and the dynamic type helps to find the most
specific implementation. In that case, both unambiguity and
extensibility are preserved. 
\textit{Hierarchical overriding} allows method overriding to be applied
only to one branch of the class hierarchy. Hierarchical overriding 
adds expressive power that is not available in languages such as 
C++ or C\#. To present both ideas, we introduce a
formalized model \MIM{} in Section~\ref{sec:formalization} based on
Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
proofs for type soundness.
